Model-based Clustering for Neural Populations

### 2021-08-30 documents/cluster_neural_population.tex
modify documents
add some reading lists for DPMM

	\item
	Larger dataset (50 neurons each):\\
	\begin{enumerate}
		\def\labelenumi{\alph{enumi}.}
		\item
		Fit by FMM with \(\mathbf{J} = 3\), start from random cluster assignments:
		\href{https://github.com/weigcdsb/state-space-clustering/blob/main/results/gif/noA_50_MM_above.gif}{GIF result 7}
		\item
		Fit by FMM with \(\mathbf{J} = 3\), start from single cluster:
		\href{https://github.com/weigcdsb/state-space-clustering/blob/main/results/gif/noA_50_MM_below.gif}{GIF result 8}
		\item
		Fit by DP (\(\alpha = 1\)), start from random assignment for 10 clusters:
		\href{https://github.com/weigcdsb/state-space-clustering/blob/main/results/gif/noA_50_DP_above1.gif}{GIF result 9}
	\end{enumerate}
\end{enumerate}

@@

\section{TODO}
\begin{enumerate}
	\def\labelenumi{(\arabic{enumi})}
	\item
	Find a more efficient way to generate new cluster parameters, otherwise the newly generated ones will always be rejected.
	\item
	improve DPMM
\end{enumerate}

>>>>

	\item
	Larger dataset (50 neurons each):\\
	\begin{enumerate}
		\def\labelenumi{\alph{enumi}.}
		\item
		Fit by FMM with \(J = 3\), start from random cluster assignments:
		\href{https://github.com/weigcdsb/state-space-clustering/blob/main/results/gif/noA_50_MM_above.gif}{GIF result 7}
		\item
		Fit by FMM with \(J = 3\), start from single cluster:
		\href{https://github.com/weigcdsb/state-space-clustering/blob/main/results/gif/noA_50_MM_below.gif}{GIF result 8}
		\item
		Fit by DP (\(\alpha = 1\)), start from random assignment for 10 clusters:
		\href{https://github.com/weigcdsb/state-space-clustering/blob/main/results/gif/noA_50_DP_above1.gif}{GIF result 9}
	\end{enumerate}
\end{enumerate}

@@

\section{TODO}
\begin{enumerate}
	\def\labelenumi{(\arabic{enumi})}
	\item
	Find a more efficient way to generate new cluster parameters, otherwise the newly generated ones will always be rejected.
	\item
	improve DPMM. In current brute force implementation, the number of potential clusters can even go beyond number of neurons (\(N\)). There are several improvements, e.g. \href{https://link.springer.com/article/10.1007/s11222-009-9150-y}{Kalli et al., 2011}, \href{http://proceedings.mlr.press/v37/gea15.html}{Ge et al., 2015} and \href{https://link.springer.com/article/10.1007/s11222-014-9471-3}{Hastie et al, 2015}. Check them later.
\end{enumerate}
